\vspace{1.0cm} \Large \bf Supplemental material of ``Health and disease imprinted in the time variability of the human microbiome''

### 2016-12-23 mSystems/rev/mSys_discussion_rev.tex
Minor changes which lead to REVISION draft E
Changes to be committed:
	modified:   rev/mSys_MAIN_rev.pdf
	modified:   rev/mSys_MAIN_rev.tex
	modified:   rev/mSys_discussion_rev.tex
	modified:   rev/mSys_suppl_rev.pdf
	modified:   rev/mSys_suppl_rev.tex

\begin{supfig}
	\centering
	%\vspace*{-10mm} % Corrects overbox of the figures
	\includegraphics[width=0.99\textwidth]{figs/supfig_HLS_xWSummary.eps}
	\caption{Taylor's law parameter space for intervals concerning gut microbiota in the host lifestyle study\cite{hostlife}. We observe that the subject B, who suffered a Salmonella infection during the experiment, had a relevant shift in the parameters from \emph{\_before} to \emph{\_infection} and a final recovery from the perturbed state to \emph{\_afterinfec}. The subject A also had a shift in the variability from \emph{\_before} to \emph{\_abroad} and back to \emph{\_returned}.}
	\label{supfig:HLS_xWSummary}
\end{supfig}

>>>>

\begin{supfig}
	\centering
	%\vspace*{-10mm} % Corrects overbox of the figures
	\includegraphics[width=0.99\textwidth]{figs/supfig_HLS_xWSummary.eps}
	\caption{Taylor's law parameter space for intervals concerning gut microbiota in the host lifestyle study\cite{hostlife}. We observe that the subject B, who suffered a Salmonella infection during the experiment, had a relevant shift in the parameters from \emph{\_before} to \emph{\_infection} and a final recovery from the perturbed state to \emph{\_afterinfec}, which lays in the parameters area compatible with the healthy and stable intervals (see Supplementary Table S7). The subject A also had a shift in the variability from \emph{\_before} to \emph{\_abroad} and back to \emph{\_returned}, also in the proximity zone of healthy and stable periods.}
	\label{supfig:HLS_xWSummary}
\end{supfig}
